### 2022-06-01 src/text/2-package-subsections/estimators.tex

Signifiance is estimated based on hypothesis \
testing agains the background only model. This allows
to assign a significance to the given flux bin.
In addition to the best fit flux norm all estimators compute
quantities corresponding to this flux. This includes
the predicted number of total, signal and background
counts per flux bin. The total fit statistics
of the best fit model, the fit statistics of the
null hypothesis and the difference between both.
From the difference in test statistics the significance
of the flux can be derived.

Optionally it can also compute more advanced qunatities
such as assymmetric flux errors, flux upper limits
and one dimensional profiles of the fit statistic,
which show how the likelihood surface varies with
the flux norm parameter around the fit minimum.
This information is useful  for inspecting the quality
of the fit, where for  sane fir a parabolic
shape of the profile is expected (see modeling / fitting section).

@@

So far \gammapy does not support "unfolding" of \gammaray spectra.
Methods for this will be implement in future version of \gammapy.

>>>>

Signifiance is estimated based on hypothesis \
testing against the background only model. This allows
to assign a significance to the given flux bin.
In addition to the best fit flux norm all estimators compute
quantities corresponding to this flux. This includes
the predicted number of total, signal and background
counts per flux bin. The total fit statistics
of the best fit model, the fit statistics of the
null hypothesis and the difference between both,
the so-called TS value.
From the TS value the significance of the
significance of the measured signal and associated flux
can be derived.

Optionally it can also compute more advanced quantities
such as assymmetric flux errors, flux upper limits
and one dimensional profiles of the fit statistic,
which show how the likelihood functions varies with
the flux norm parameter around the fit minimum.
This information is useful for inspecting the quality
of the fit, where assumptoticcally a parabolic
shape of the profile is expected at the best fit
values (\todo{Reference to modeling / fitting section?}).

@@

So far \gammapy does not support "unfolding" of \gammaray spectra.
Methods for this will be implemented in future version of \gammapy.
